A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2019-04-25 for_submission/rvaught_2018.tex

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.57]{figure11.pdf}%all_limitsv2.pdf
\caption{Comparison of our detection limits to the SB, measured in two independent locations spatially offset from the galaxy continuum, of extended \ion{Mg}{2} emission around the starburst galaxy TKRS 4389 \textbf{and one independent location spatially offset from the galaxy continuum eastward of 32016857}. These surface brightness constraints are plotted vs.\ SFR (left), stellar mass (middle), and specific SFR (right). Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389 with SFR $\sim 50 \msunperyr$ and 32016857 with SFR $\sim 80 \msunperyr$. The symbol colors indicate the same galaxies as in Figure \ref{fig:ew_comb}}
\label{fig:all_limits}
\end{figure*}

>>>>

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.57]{figure11.pdf}%all_limitsv2.pdf
\caption{Comparison of our detection limits to the SB of extended \ion{Mg}{2} emission measured in two independent locations spatially offset from the continuum around the starburst galaxy TKRS 4389 (reported by \citealt{Rubin_2011}), \textbf{and in one location spatially offset from the continuum eastward of the star-forming galaxy 32016857 (reported by \citealt{Martin2013})}. These surface brightness constraints are plotted vs.\ SFR (left), stellar mass (middle), and specific SFR (right). Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389 with SFR $\sim 50 \msunperyr$ and 32016857 with SFR $\sim 80 \msunperyr$. The symbol colors indicate the same galaxies as in Figure \ref{fig:ew_comb}.}
\label{fig:all_limits}
\end{figure*}
